Appendix B: Examples of Deep RL in Ecological Decision Problems

### 2021-05-27 appendices/appendix-B-examples.Rmd
WIP

# Optionally set to "" to force CPU-evaluation if needing perfect reproducibility
Sys.setenv("CUDA_VISIBLE_DEVICES"="")
set.seed(seed)
```

@@

```{r}
sims_df <- opt_sims %>% mutate(model = "1_optimal")
policy_df <- opt_policy  %>% mutate(model = "1_optimal")

@@

```{r}
if(!file.exists("cache/a2c.zip")) {

@@

  # Save our trained agent for future use
  a2c$save("cache/a2c")
}
```

@@

```{r}
# Simulate management under the trained agent
a2c = sb3$A2C$load("cache/a2c")
```

@@

```{r}
sims_df <- a2c_sims %>% mutate(model = "A2C") %>% bind_rows(sims_df)
policy_df <- a2c_policy  %>% mutate(model = "A2C")  %>% bind_rows(policy_df)

@@

```{r}
sims_df <- td3_sims_untuned %>% mutate(model = "TD3_untuned") %>% bind_rows(sims_df)
policy_df <- td3_policy_untuned  %>% mutate(model = "TD3_untuned")  %>% bind_rows(policy_df)

@@

```{r }
if(!file.exists("cache/td3.zip")){

  td3$learn(total_timesteps=300000L)
  td3$save("cache/td3")

@@

```{r}
# Simulate management under the trained agent
td3 = sb3$TD3$load("cache/td3")
td3_sims = env$simulate(td3, reps = 100L)
td3_policy = env$policyfn(td3, reps = 5L)
```

```{r}
sims_df <- td3_sims %>% mutate(model = "TD3") %>% bind_rows(sims_df)
policy_df <- td3_policy  %>% mutate(model = "TD3")  %>% bind_rows(policy_df)

@@

```{r}
env = gym$make("conservation-v6")
```

```{r}
noise_std = 0.4805935357322933

OU = sb3$common$noise$OrnsteinUhlenbeckActionNoise
action_noise = OU(mean = np$zeros(1L),  sigma = noise_std * np$ones(1L))

@@

```{r}
if(!file.exists("cache/td3-conservation.zip")){

  model$learn(total_timesteps=3000000L)
  model$save("cache/td3-conservation")

@@

model = sb3$TD3$load("cache/td3-conservation")
TD3_sims = env$simulate(model, reps = 100L)
TD3_policy = env$policyfn(model, reps = 10L)
```

@@

>>>>

# Optionally set to "" to force CPU-evaluation if needing perfect reproducibility
#Sys.setenv("CUDA_VISIBLE_DEVICES"="")
set.seed(seed)
```

@@

```{r}
algos <- c("Optimal", "A2C", "TD3", "TD3_tuned")
sims_df <- opt_sims %>% mutate(model = factor("Optimal", algos))
policy_df <- opt_policy  %>% mutate(model = factor("Optimal", algos))

@@

```{r}
if(!file.exists("../python/cache/a2c.zip")) {

@@

  # Save our trained agent for future use
  a2c$save("../python/cache/a2c")
}
```

@@

```{r}
# Simulate management under the trained agent
a2c = sb3$A2C$load("../python/cache/a2c")
```

@@

```{r}
sims_df <- a2c_sims %>% mutate(model = factor("A2C", algos)) %>% bind_rows(sims_df)
policy_df <- a2c_policy  %>% mutate(model = factor("A2C", algos))  %>% bind_rows(policy_df)

@@

```{r}
sims_df <- td3_sims_untuned %>% mutate(model = factor("TD3", algos)) %>% bind_rows(sims_df)
policy_df <- td3_policy_untuned  %>% mutate(model = factor("TD3", algos))  %>% bind_rows(policy_df)

@@

```{r }
if(!file.exists("../python/cache/td3_tuned.zip")){

  td3$learn(total_timesteps=300000L)
  td3$save("../python/cache/td3_tuned")

@@

```{r}
# Simulate management under the trained agent
td3 = sb3$TD3$load("../python/cache/td3_tuned")
td3_sims = env$simulate(td3, reps = 100L)
td3_policy = env$policyfn(td3, reps = 5L)
```

```{r}
sims_df <- td3_sims %>% mutate(model = factor("TD3_tuned", algos)) %>% bind_rows(sims_df)
policy_df <- td3_policy  %>% mutate(model = factor("TD3_tuned", algos))  %>% bind_rows(policy_df)

@@

```{r}
# Python users see python/conservation_TD3.py
env = gym$make("conservation-v6")

noise_std = 0.4805935357322933
OU = sb3$common$noise$OrnsteinUhlenbeckActionNoise
action_noise = OU(mean = np$zeros(1L),  sigma = noise_std * np$ones(1L))

@@

As before, we train the agent unless a cached version of the trained agent is already available:

```{r}
if(!file.exists("../python/cache/td3-conservation.zip")){

  model$learn(total_timesteps=3000000L)
  model$save("../python/cache/td3-conservation")

@@

model = sb3$TD3$load("../python/cache/td3-conservation")
TD3_sims = env$simulate(model, reps = 100L)
TD3_policy = env$policyfn(model, reps = 10L)
```

@@

```{r}
```
